Two Problems for Sophistication

### 2015-07-09 Facticity/Facticity/paper.tex
...

\author{Peter Bloem and Steven de Rooij}

\institute{
  System and Network Engineering Group, \\University of Amsterdam, the Netherlands\\
  \email{uva@peterbloem.nl, steven.de.rooij@gmail.com}
}

@@

\section{Introduction}
\enlargethispage{2\baselineskip}
\footnotetext{Peter Bloem is a student author (PhD student).}

@@

For technical reasons, we deviate slightly from the traditional notation of Kolmogorov complexity: we define the $\M$-Kolmogorov complexity of a binary string $x$, with respect to a model class $\M$ and a numbering $\psi$, as follows $C^{\M,\psi}(x\mid z)=\min\{\bar\imath y:\psi_i(y; z)=x,i\in\M\}$, with $C^{\M,\psi}(x) = C^{\M,\psi}(x\mid \epsilon)$. We may drop the numbering parameter when the distinction isn't relevant. Under this notation $C^\C(x)$ corresponds to the plain Kolmogorov complexity $C(x)$ and $C^\K(x)$ corresponds to the prefix-free version $K(x)$. We can also represent the smallest two-part description of $x$ using a given model $\phi_i$ as $C^{\{i\}}(x)$. The complexity of a finite set is defined an the complexity of an explicit enumeration.

@@

\subsubsection*{\ackname}

This publication was supported by the Dutch national program COMMIT and by  the Netherlands eScience center. We thank Tom Sterkenburg for interesting discussions.

>>>>

\author{\ldots}

%institute{
%  System and Network Engineering Group, \\University of Amsterdam, the Netherlands\\
%  \email{uva@peterbloem.nl, steven.de.rooij@gmail.com}
%}

@@

\section{Introduction}
\enlargethispage{2\baselineskip}

@@

For technical reasons, we deviate slightly from the traditional notation of Kolmogorov complexity: we define the $\M$-Kolmogorov complexity of a binary string $x$, with respect to a model class $\M$ and a numbering $\psi$, as follows $C^{\M,\psi}(x\mid z)=\min\{\bar\imath y:\psi_i(y; z)=x,i\in\M\}$, with $C^{\M,\psi}(x) = C^{\M,\psi}(x\mid \epsilon)$. We may drop the numbering parameter when the distinction is not relevant. Under this notation $C^\C(x)$ corresponds to the plain Kolmogorov complexity $C(x)$ and $C^\K(x)$ corresponds to the prefix-free version $K(x)$. We can also represent the smallest two-part description of $x$ using a given model $\phi_i$ as $C^{\{i\}}(x)$. The complexity of a finite set is defined an the complexity of an explicit enumeration.

@@

\subsubsection*{\ackname}
\ldots
\hide{This publication was supported by the Dutch national program COMMIT and by  the Netherlands eScience center. We thank Tom Sterkenburg for interesting discussions.}
